The expected shape of the Milky Way's Dark Matter halo

### 2018-10-12 Paper/paper.tex

All these difficulties (enough numerical resolution, explicit
cosmological context, appropriate feedback physics to produce
realistic MW disks) have limited the studies that want to study the
rounding effect of baryons in MW-like galaxies.

In this work we overcome these three limitation by analyzing the
Our objective is to quantify the DM halo shape and investigate the
effect of baryons.

%Better connector with observations of distant galaxies. Gravitational
%lensing and star tracers. (Talk about discrepancy with simulations,
%perhaps later) and state that the preference for axisymmetrical shapes
%may arise from the observational restrictions (projection) look for
%citations about this.

@@

\bibliographystyle{mnras}
\bibliography{references}

@@

@@

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
\end{document}

>>>>

All these difficulties (enough numerical resolution, explicit
cosmological context, appropriate feedback physics to produce
realistic MW disks) have limited the studies that want to study the
rounding effect of baryons in MW-like galaxies.
In this work we overcome these three limitation by analyzing the
results of state-of-the-art hydrodynamical simulations of isolated
halos that resemble the Milky Way.

@@

@@

 \bibliographystyle{mnras}
 \bibliography{references}
\end{document}

@@

% Don't change these lines
\bsp	% typesetting comment
\label{lastpage}
